\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-16 icse/compiler.tex
Revised section 4 except 4.4

In this section, we propose the \textit{algorithm compiler}
that compiles abstract algorithms into \( \ires \) functions
and its overall structure is described in Figure~\ref{fig:algo-compiler}.
Before compiling abstract algorithms,
the tokenizer first tokenizes each abstract algorithm into
a list of tagged tokens. Then, the token parser constructs
syntactic parse tree of the given token list.
Finally, the \( \ires \) function generator constructs the corresponding
\( \ires \) function from the given parse tree.
The parser and the generator is dependent on conversion rules
and we define the general conversion rules for abstract algorithms in
ECMAScript specifications. Like Coq, a proof assistant, we also provide
the \textit{rule generation assistant} to make easy write conversion rules.
It suggests new conversion rules based on
statistical analysis of algorithm steps that failed to be parsed
and also diagnoses root causes of parsing failures.

@@

Abstract algorithms in ECMAScript specifications are written in structured
natural languages in HTML files. An algorithm consists of ordered steps
and it might contain sub-steps as well. For example,
the \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive-es}
has three steps and second step has seven sub-steps.
Moreover, the tokens of each step has its own HTML tag and each tag
has the following meaning:
\[
  \begin{array}{c|l}
    \text{HTML tags} & \text{meanings}\\\hline\hline
    \code{<var>} & \text{variables}\\\hline
    \code{<emu-grammar>} & \text{productions}\\\hline
    \code{<emu-nt>} & \text{non-terminal syntax}\\\hline
    \code{<code>} & \text{ECMAScript codes}\\\hline
    \code{<emu-const>} & \text{constant values}\\\hline
    \code{<emu-val>} & \text{values}\\\hline
    \code{<ol>} & \text{ordered sub-steps}\\\hline
    \code{<ul>} & \text{unordered sub-steps}\\\hline
    \code{<sup>} & \text{superscripts}\\\hline
    \text{otherwise} & \text{simple texts}\\\hline
  \end{array}
\]
We try to keep the tag information for each token to generate more
precise conversion rules. For example, if and only if a token has a tag
\( \code{<var>} \), it is a parameter or a local variable.
Thus, it is possible to construct a conversion rule precisely discriminates
identifiers and other components.

The tokenizer first recognizes the overall structures of steps.
Then, it divides each step into sequence of tagged tokens.
If an HTML element has a explicit tag, it is converted into a single token
with the tag. Otherwise, it is divided into multiple tokens and each token
should be a sequence of alphanumeric characters or a single
non-alphanumeric character. For example, in the \( \code{ToPrimitive} \)algorithm,
\( \textbf{\code{"default"}} \) is a single token with the tag \( \code{<code>} \)
and \( \code{@@toPrimitive} \) is divided into three text tokens
\( \code{@} \), \( \code{@} \), and \( \code{toPrimitive} \).

For the linear structures, the tokenizer flatten the structured steps into
a single list. Some conversion rules should handle multiple steps such as
the conditional statements (if-then-else). Thus, we decide to break down
structured algorithms using three special tokens;
\( \tend \) denotes the end of a single step,
\( \tin \) and \( \tout \) the start and the end of nested steps, respectively.
For example, the \( \code{ToPrimitive} \) algorithm is tokenized as follows.
\[
  \begin{array}{l}
    \code{Assert} \cdots \tend\\
    \code{If} \cdots \tin \code{If} \cdots \tend
    \cdots \code{Return} \cdots \tend \tout \tend\\
    \code{Return} \cdots \tend\\
  \end{array}
\]

\subsection{Token Parser}

The token parser parses a given list of tokens into a syntactic parse tree.
It depends on the given \textit{conversion rules} that consists of
two parts parsing rules and mapping from parsing rules into corresponding
\( \ires \) components.
A parsing rule consists of basic token matchers and other parsing rules
including itself. For example, the following parsing rule is simplified version for
sub-step \( i \) in the \( \code{ToPrimitive} \) algorithm.
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = "Let" ~ varT ~ "be" ~ Expr ~ "." ^^ ...
// expressions
val Expr = (
  // identifiers
  varT ^^ ... |
  // return if abrupt
  "?" ~ Expr ^^ ... |
  // function calls
  textT ~ "(" ~ repsep(varT, ",") ~ ")" ^^ ... |
  // lists
  "<<" ~ repsep(Expr, ",") ~ ">>" ^^ ...
)
\end{lstlisting}

Each parsing rule is written in extended Scala parser combinators.
We modify the meaning of alternative composition operator ( \( | \) ) to collect
all longest matched results. If the parser detects that a step cannot be
parsed with the given parsing rules. It reports that a step is not possible
to be parsed under the given rules into the rule generation assistant.
Moreover, even though the parser could parse a step, it will be also reported
if it could be parsed in not a single but multiple ways.
Each string literal is a token matcher for tokens without any tags and checks
that the token has same string value with the string literal.
The \( \code{varT} \) and \( \code{textT} \) is also token matchers
for token with the tag \( \code{<var>} \) and no tags.
The \( \code{Step} \) and \( \code{Expr} \) are user-defined parsing rules
defined with our extended parser combinators.
Moreover, it supports all helpers functions defined in Scala parser combinators.
For example, the helper function \( \code{repsep(p, q)} \) generates a new
parsing rule that denotes zero or more repetitions of the parsing rule \( \code{p} \)
using another parsing rule \( \code{q} \) as separators.
Finally, the token parser with the above rules parses sub-step \( i \) in the
\( \code{ToPrimitive} \) into the following syntactic parse tree:
\includegraphics[width=0.5\textwidth]{img/token_ast.png}

\subsection{\( \ires \) Function Generator}

We define \( \ires \) language to give semantics into syntactic parse tree of
abstract algorithm steps. It has the following language features:

\begin{itemize}
\item \textbf{Dynamic Typing} We decide to use dynamic typing for \( \ires \)
because each variables in abstract algorithms are not statically typed.
Thus, variables do not have its own static types while each value of \( \ires \)
has its dynamic type.

\item \textbf{Imperative Style} \( \ires \) represents algorithm steps
as statements. Each statement changes the current state
that consists of environments and a heap.

\item \textbf{Higher-order Functions with Restricted Scopes} \( \ires \) supports
lambda functions as values but it has only restricted scopes. In each function,
only global variables, parameter, and newly defined local variables are accessible.
It means that the function closure does not capture the the current environment.
We use such restricted scopes because it is enough to represent abstract algorithms.

\item \textbf{Primitive Values} \( \ires \) supports ECMAScript primitive values except
the symbols that is newly introduced after ECMAScript 6. Thus, only five ECMAScript primitives
are defined in \( \ires \); numbers, strings, booleans, \( \code{undefined} \), and \( \code{null} \).
Moreover, \( \ires \) also supports the unique \( \code{absent} \) value to represent
the absence of parameters. For example, the second parameter \( \code{PreferredType} \)
of \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive-es} might be
not present in some function calls. Then, the parameter has the \( \code{absent} \) value
to represent its absence.

\item \textbf{Abstract Data Types} \( \ires \) only supports three abstract data types;
\( \code{Record} \) for mapping from some values into other value,
\( \code{List} \) for sequential data types,
and \( \code{Singleton} \) for singleton data types.
They are stored in corresponding addresses in the heap structure.
For example, ECMAScript environment records are represented as \( \code{Record} \) data types
from String values for identifier names into addresses.
The addresses point to other \( \code{Record} \) data types that represent ECMAScript bindings.
We treat a ECMAScript constants such as \( \code{empty} \) and primitive symbols as singleton
data types in \( \ires \).
\end{itemize}

To generate the corresponding \( \ires \) function from syntactic parse tree,
we describe the mapping from each parsing rule into the corresponding \( \ires \) components.
For example, we describe the following mapping for the previous example parsing rules:
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = ... ^^ { case _ ~ x ~ _ ~ y => ESLet(x, y) }
// expressions
val Expr = (
  // identifiers
  ... ^^ { x => x } |
  // return if abrupt
  ... ^^ { _ ~ e => ESReturnIfAbrupt(e) } |
  // function calls
  ... ^^ { case x ~ _ ~ y ~ _ => ESCall(x, y) } |
  // lists
  ... ^^ { case _ ~ x ~ _ => ESList(e) }
)
\end{lstlisting}
Finally, sub-step \( i \) in the \( \code{ToPrimitive} \) is converted
into the following instruction:
\begin{lstlisting}[style=ires]
let result = ? (Call exoticToPrim input (new [hint]))
\end{lstlisting}

@@

\inred{
To make easy write conversion rules, we support \textit{rule generation assistant}.
It consists of two helper functions; the \textit{rule recommender} and
the \textit{fault localizer}. The

It makes easy not only construct conversion rules from the scratch
but also updates existing conversion rules to handle specification updates.
We explain each helper function and how to utilize it to construct conversion rules.

>>>>

In this section, we propose the \textit{algorithm compiler}
that compiles abstract algorithms into \( \ires \) functions
and its overall structure is described in Figure~\ref{fig:algo-compiler}.
Before compiling abstract algorithms,
the tokenizer first tokenizes each abstract algorithm into
a list of tagged tokens. Then, the token parser constructs
abstract syntax tree (AST) of the given token list.
Finally, the \( \ires \) matcher constructs the corresponding
\( \ires \) function from the given token AST.
The parser and the matcher are dependent on compile rules
and we define the general compile rules for abstract algorithms in
ECMAScript specifications. Like Coq, a proof assistant, we also provide
the \textit{rule assistant} to make easy write compile rules.
It suggests new compile rules based on
statistical analysis of failed algorithm steps to be parsed
and also diagnoses root causes of parsing failures
for updated abstract algorithms.

@@

Abstract algorithms in ECMAScript specifications are written in structured
natural languages in HTML files. An algorithm consists of ordered steps
and it might contain sub-steps as well. For example,
the ToPrimitive algorithm in Figure~\ref{fig:to-primitive-es}
has three steps and second step has seven sub-steps.
Moreover, the tokens of each step has its own HTML tag and each tag
has the following meaning:
\[
  \begin{array}{c|l}
    \text{HTML tags} & \text{meanings}\\\hline\hline
    \code{<var>} & \text{variables}\\\hline
    \code{<emu-grammar>} & \text{productions}\\\hline
    \code{<emu-nt>} & \text{non-terminal syntax}\\\hline
    \code{<code>} & \text{ECMAScript codes}\\\hline
    \code{<emu-const>} & \text{constant values}\\\hline
    \code{<emu-val>} & \text{values}\\\hline
    \code{<ol>} & \text{ordered sub-steps}\\\hline
    \code{<ul>} & \text{unordered sub-steps}\\\hline
    \code{<sup>} & \text{superscripts}\\\hline
    \text{otherwise} & \text{simple texts}\\\hline
  \end{array}
\]
We try to keep the tag information for each token to generate more
precise compile rules. For example, if and only if a token has a tag
\( \code{<var>} \), it is a parameter or a local variable.
Thus, it is possible to construct a compile rule precisely discriminates
identifiers and other components.

The tokenizer first recognizes the overall structures of steps.
Then, it divides each step into sequence of tagged tokens.
If an HTML element has a explicit tag, it is converted into a single token
with the tag. Otherwise, it is divided into multiple tokens and each token
should be a sequence of alphanumeric characters or a single
non-alphanumeric character. For example, in the ToPrimitive algorithm,
\( \textbf{\code{"default"}} \) is a single token with the HTML tag \( \code{<code>} \)
and \( \code{@@toPrimitive} \) is divided into three text tokens
\( \code{@} \), \( \code{@} \), and \( \code{toPrimitive} \).

Moreover, the tokenizer flattens the structured steps into
a single token list to easily handle multi-step statements.
Several statements in abstract algorithms consists of multilple steps.
For example, an if-then-else statement often consists of two steps;
one step for the then-branch and another step for the else-branh.
For linear structures, we introduce three special tokens to break down structured
algorithms; \( \tend \) denotes the end of a single step,
\( \tin \) and \( \tout \) the start and the end of nested steps, respectively.
For example, the ToPrimitive algorithm is tokenized as follows.
\[
  \begin{array}{l}
    \code{Assert} \cdots \tend\\
    \code{If} \cdots \tin \code{If} \cdots \tend
    \cdots \code{Return} \cdots \tend \tout \tend\\
    \code{Return} \cdots \tend\\
  \end{array}
\]

After tokenizing abstract algorithms, the algorithm compiler compiles token lists
into \( \ires \) functions. It consists of two modules; the token list parser and
the token AST converter. They are dependent on compile rules and each compile rule
consists of a \textit{parsing rule} and a \textit{conversion rule}:
\begin{lstlisting}[style=myScalastyle]
val CompileRule = ParsingRule ^^ ConversionRule
\end{lstlisting}
For the compile rule \( \code{CompileRule} \), the parsing rule
\( \code{ParsingRule} \) describes how to parse the given token list into structured
token AST. The conversion rule \( \code{ConversionRule} \) describes how to
convert the given token AST structure into an \( \ires \) component.
Now, we explain the token list parser and token AST converter with
parsing rules and conversion rules, respectively.

\subsection{Token List Parser}

The token list parser is dependent on the given parsing rules.
Each parsing rule is written in extended Scala parser combinators.
We modify the meaning of alternative composition operator ( \( | \) ) to collect
all longest matched results. If the parser detects that a step cannot be
parsed with the given parsing rules. It reports that the step is not possible
to be parsed under the given rules into the rule assistant.
Moreover, even though the parser could parse the step, it will be also reported
if it could be parsed in not a single but multiple ways.
We basically use Packrat parsing~\cite{packrat}, the parsing rule could support
not only non-left recursive but also left recursive parsing rules.

We support two kinds of basic token parsers; tag-based parsers and
content-based parsers. A tag-based parser just checks that the next
token has the given tag. For example, the tag-based parser \( \code{varT} \)
checks that the next token has the tag \( \code{<var>} \). A content-based parser
checks that the next token is text token and its content passes the given condition.
For example, the String literal \( \code{"Let"} \) denotes the content parser
that checks whether the next token is text token with the content \( \code{Let} \).
Moreover, we provide two content parsers \( \code{word} \) and \( \code{number} \)
that checks the content consists of only alphabets or numbers, respectively.
In the parsing rule, any helper functions defined in Scala parser combinators
are available. For example, the helper function \( \code{repsep(p, q)} \) generates a new
parsing rule that denotes zero or more repetitions of the parsing rule \( \code{p} \)
using another parsing rule \( \code{q} \) as the separator.

For example, the following parsing rule is simplified version for
the step 2-e-i of the ToPrimitive algorithm.
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = "Let" ~ varT ~ "be" ~ Expr ~ "." ^^ ...
// expressions
val Expr = (
  // identifiers
  varT ^^ ... |
  // return if abrupt
  "?" ~ Expr ^^ ... |
  // function calls
  word ~ "(" ~ repsep(varT, ",") ~ ")" ^^ ... |
  // lists
  "<<" ~ repsep(Expr, ",") ~ ">>" ^^ ...
)
\end{lstlisting}
The \( \code{Stmt} \) denotes the compile rule for statements with one
parsing rule. The \( \code{Expr} \) represents the compile rule for expressions
with four different parsing rules. Finally, the token parser with the above rules
parses the step 2-e-i in the ToPrimitive into the following
token AST:
\begin{center}
\includegraphics[width=0.5\textwidth]{img/token_ast.png}
\end{center}

\subsection{Token AST Converter}

We define \( \ires \) to represent abstract algorithms as its functions.
The following bullets explain the reason of our language design choices
for \( \ires \).

\begin{itemize}
\item \textbf{Dynamic Typing} We decide to use dynamic typing for \( \ires \)
because each variable in abstract algorithms are not statically typed.
Thus, variables do not have its own static types while each value of \( \ires \)
has its dynamic type.

\item \textbf{Imperative Style} \( \ires \) represents algorithm steps
as imperative-style instructions. Each instruction changes the current state
that consists of an environment and a heap.

\item \textbf{Higher-order Functions with Restricted Scopes} \( \ires \) supports
lambda functions as values but they have only restricted scopes. In each function,
only global variables, parameters, and newly defined local variables are available.
It means that the function closure does not capture the current environment.
We use such restricted scopes because it is enough to represent abstract algorithms.

\item \textbf{Primitive Values} \( \ires \) supports ECMAScript primitive values except
the symbols that is newly introduced after ECMAScript 6. In JavaScript, symbols are
primitive values but it is much easier to treat them as singleton objects.
Thus, only five ECMAScript primitives are defined in \( \ires \);
numbers, strings, booleans, \( \code{undefined} \), and \( \code{null} \).
Moreover, \( \ires \) also supports the unique \( \code{absent} \) value to represent
the absence of parameters. For example, the second parameter \( \code{PreferredType} \)
of ToPrimitive algorithm in Figure~\ref{fig:to-primitive-es} might be
not present in some function calls. Then, the parameter has the \( \code{absent} \) value
to represent its absence.

\item \textbf{Abstract Data Types} \( \ires \) only supports three abstract data types;
\( \code{Record} \) for mapping from some values into other value,
\( \code{List} \) for sequential data types,
and \( \code{Singleton} \) for singleton data types.
They are stored in corresponding addresses in the heap structure.
For example, ECMAScript environment records are represented as \( \code{Record} \) data types
String values as keys and addresses as values. Each key String value represents an identifier
name and each address represents an ECMAScript binding object.
Thus, the addresses point to other \( \code{Record} \) data types that represent ECMAScript bindings
in the heap. We treat not only symbols but also constants used in ECMAScript specifications,
such as \( \code{empty} \) or \( \code{normal} \), as singleton data types in \( \ires \).
\end{itemize}

To generate the corresponding \( \ires \) function from the given token AST,
the token AST converter uses the given coversion rules. Each conversion rule is
defined with the corresponding parsing rule and it is a function from given token AST
into an \( \ires \) component. For basic token parsers, their conversion rules
always return the String value of the content in the parsed token.
For example, the following conversion rules are for the previous example
parsing rules:
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = ... ^^ { case _ ~ x ~ _ ~ y => ILet(x, y) }
// expressions
val Expr = (
  // identifiers
  ... ^^ { x => EId(x) } |
  // return if abrupt
  ... ^^ { _ ~ e => EReturnIfAbrupt(e) } |
  // function calls
  ... ^^ { case x ~ _ ~ y ~ _ => ECall(x, y) } |
  // lists
  ... ^^ { case _ ~ x ~ _ => EList(e) }
)
\end{lstlisting}
The conversion rule of the compile rule \( \code{Stmt} \) takes
only second and fourth sub trees and convert them into \( \ires \) components.
The second sub-tree is converted into a String value because it was
constructed via basic the token parser \( \code{varT} \).
The fourth sub-tree is converted into an \( \ires \) expression
because the conversion rules of the \( \code{Expr} \) compile rule
constructs \( \ires \) expressions.
Then, the conversion rule of \( \code{Stmt} \) constructs the
lexical binding instruction \( \code{ILet} \) with the String value
and the \( \ires \) expression. Finally, sub-step 2-e-i in the ToPrimitive
is converted into the following instruction:
\begin{lstlisting}[style=ires]
let result = ? (Call exoticToPrim input (new [hint]))
\end{lstlisting}

@@

\inred{
To make easy write compile rules, we support \textit{rule generation assistant}.
It consists of two helper functions; the \textit{rule recommender} and
the \textit{fault localizer}. The

It makes easy not only construct compile rules from the scratch
but also updates existing compile rules to handle specification updates.
We explain each helper function and how to utilize it to construct compile rules.

### 2019-08-16 icse/eval.tex
Revised section 4 except 4.4

\begin{itemize}
  \item RQ1) Does \( \tool \) correctly extract semantics? \inred{ES2020 / test262 coverage - parser / semantics}
    test262 결과를 어떻게? 전체 개수 / applicable tests 개수 / succes, fail 개수
  \item RQ2) Is endurable size of manual portion in implementation of \( \tool \)? \inred{refactoring for conversion rules / get statistics of conversion rules}
    개수만 - stmt / expr / cond / ref 몇개씩? / corner cases 개수
  \item RQ3) Does \( \tool \) deal with annual updates from small changes? \inred{proposed language features / related tests in test262 / diff of conversion rules}
    각 feature name / 의미 / compile 성공률 / 결과 test
  \item RQ4) How many specification errors are detected by \( \tool \)? \inred{supprot "Assert: ... "?/ confirm found spec errors by TC39}
\end{itemize}

>>>>

\begin{itemize}
  \item RQ1) Does \( \tool \) correctly extract semantics? \inred{ES2020 / test262 coverage - parser / semantics}
    test262 결과를 어떻게? 전체 개수 / applicable tests 개수 / succes, fail 개수
  \item RQ2) Is endurable size of manual portion in implementation of \( \tool \)? \inred{refactoring for compile rules / get statistics of compile rules}
    개수만 - stmt / expr / cond / ref 몇개씩? / corner cases 개수
  \item RQ3) Does \( \tool \) deal with annual updates from small changes? \inred{proposed language features / related tests in test262 / diff of compile rules}
    각 feature name / 의미 / compile 성공률 / 결과 test
  \item RQ4) How many specification errors are detected by \( \tool \)? \inred{supprot "Assert: ... "?/ confirm found spec errors by TC39}
\end{itemize}

### 2019-08-16 icse/intro.tex
Revised section 4 except 4.4

In this paper, we propose JavaScript IR-based Semantics Extraction Toolchain (\( \tool \))
based on ECMAScript specifications. The tool automatically extracts JavaScript
syntax and semantics from ECMAScript specifications. It generates JavaScript parser
from the syntax provided by ECMAScript specifications. It also automatically extracts
formal JavaScript semantics with given \textit{conversion rules}. Each conversion
rule describes how abstract algorithms in specifications are converted into
functions of our intermediate representation \( \ires \) for ECMAScript.
However, to save the labor of defining such rules, we also propose a \textit{rule generation assistant}.
It suggests new conversion rules based on statistical analysis of not yet convertible algorithms.
The assistant helps us deal with changed or newly introduced algorithms defined in new versions of
ECMAScript specifications as well.

>>>>

In this paper, we propose JavaScript IR-based Semantics Extraction Toolchain (\( \tool \))
based on ECMAScript specifications. The tool automatically extracts JavaScript
syntax and semantics from ECMAScript specifications. It generates JavaScript parser
from the syntax provided by ECMAScript specifications. It also automatically extracts
formal JavaScript semantics with given \textit{compile rules}. Each compile
rule describes how abstract algorithms in specifications are converted into
functions of our intermediate representation \( \ires \) for ECMAScript.
However, to save the labor of defining such rules, we also propose a \textit{rule generation assistant}.
It suggests new compile rules based on statistical analysis of not yet convertible algorithms.
The assistant helps us deal with changed or newly introduced algorithms defined in new versions of
ECMAScript specifications as well.

### 2019-08-16 icse/main.tex
Revised section 4 except 4.4

To alleviate such problems, we propose \( \tool \), a JavaScript IR-based Semantics
Extraction Toolchain. It automatically extracts JavaScript syntax and semantics from ECMAScript
specifications. \( \tool \) generates JavaScript parser for the given grammar written
in \( \bnfes \), an extended BNF used in ECMAScript specifications.
Our tool also converts each abstract algorithm written in structured natural
languages into functions written in \( \ires \), an Intermediate Representation
for ECMAScript specifications. The conversion from algorithms to \( \ires \) functions
is defined with \textit{conversion rules}. We apply \( \tool \) into the next proposed
version, ECMAScript 2020. and the extracted semantics passes all \inred{XXXXX} tests
in test262, the official ECMAScript conformance test suite.
Moreover, \( \tool \) also successfully extracts semantics for \inred{XX} proposed features
by adding only \inred{XX} minor conversion rules.
\end{abstract}

>>>>

To alleviate such problems, we propose \( \tool \), a JavaScript IR-based Semantics
Extraction Toolchain. It automatically extracts JavaScript syntax and semantics from ECMAScript
specifications. \( \tool \) generates JavaScript parser for the given grammar written
in \( \bnfes \), an extended BNF used in ECMAScript specifications.
Our tool also converts each abstract algorithm written in structured natural
languages into functions written in \( \ires \), an Intermediate Representation
for ECMAScript specifications. The compilation from algorithms to \( \ires \) functions
is defined with \textit{compile rules}. We apply \( \tool \) into the next proposed
version, ECMAScript 2020. and the extracted semantics passes all \inred{XXXXX} tests
in test262, the official ECMAScript conformance test suite.
Moreover, \( \tool \) also successfully extracts semantics for \inred{XX} proposed features
by adding only \inred{XX} minor compile rules.
\end{abstract}

### 2019-08-16 icse/overview.tex
Fixed small errors
Revised section 4 except 4.4

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/array_literal.png}
    \caption{ArrayLiteral production in ECMAScript 2019 specification.}
    \label{fig:array-literal-es}
  \end{subfigure}
  \begin{subfigure}[t]{0.48\textwidth}
    \begin{lstlisting}[style=myScalastyle]
type P[T] = List[Boolean] => LAParser[T]
lazy val ArrayLiteral: P[ArrayLiteral] = memo {
  case List(Yield, Await) =>
  "[" ~ opt(Elision) ~ "]" ^^ ArrayLiteral0 |
  "[" ~ ElementList(Yield, Await) ~ "]" ^^ ArrayLiteral1 |
  "[" ~ ElementList(Yield, Await) ~ "," ~ opt(Elision) ~ "]" ^^ ArrayLiteral2
}
    \end{lstlisting}
    \caption{The generated parser for ArrayLiteral production.}
    \label{fig:array-literal-parser}
  \end{subfigure}
  \caption{ArrayLiteral grammar production in ECMAScript 2019.}
  \label{fig:array-literal}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/to_primitive.png}
    \subcaption{\( \code{ToPrimitive} \) abstract algorithm in ES2019.}
    \label{fig:to-primitive-es}
  \end{subfigure}
  \qquad
  \begin{subfigure}{0.48\textwidth}
    \begin{lstlisting}[style=ires]
"ToPrimitive" (input, PreferredType) => {
  if (= (Type input) "Object") {
    if (= PreferredType absent) let hint = "default"
    else if (= PreferredType "String") let hint = "string"
    else let hint = "number"
    let exoticToPrim = ? (GetMethod input SYMBOL_toPrimitive)
    if (! (= exoticToPrim undefined)) {
      let result = ? (Call exoticToPrim input (new [hint]))
      if (! (= (Type result) "Object")) return result
      return (Throw INTRINSIC_TypeErrorPrototype)
    }
    if (= hint "default") hint = "number"
    return ? (OrdinaryToPrimitive input hint)
  }
  return input
}
    \end{lstlisting}
    \subcaption{The \( \ires \) funciton for \( \code{ToPrimitive} \)
    abstract algorithm.}
    \label{fig:to-primitive-ires}
  \end{subfigure}
  \caption{\( \code{ToPrimitive} \) abstract algorithms
  and its generated core program.}
  \label{fig:to-primitive}
\end{figure*}

@@

The semantics in ECMAScript specifications are described as
abstract algorithms. They are written in structured natural languages
with ordered steps and tagged tokens. The spec extractor extracts each abstract algorithm
with HTML tags because we utilize tag information to discriminate different kinds of tokens.
For example, Figure~\ref{fig:to-primitive-es} is the \( \code{ToPrimitive} \)
abstract algorithm in ECMAScript 2020. It has three steps and
second step consists of seven sub-steps. Each parameter or local variable such as
\( \code{input} \) or \( \code{PreferredType} \) is written with \( \code{<var>} \) HTML tags
and each value is tagged with \( \code{<code>} \).

To extract such abstract algorithms into treatable representations,
we define \( \ires \), a specialized intermediate representation
for ECMAScript abstract algorithms. Then, we develop the \textit{algorithm compiler}
in Scala using also Scala parser combinators to convert given abstract algorithms
into \( \ires \) functions. It is dependent on the conversion rules that consists of two parts;
parsing rules and mapping from each rule into \( \ires \) component.
We explain detailed role of conversion rules in Section~\ref{sec:compiler}.
Thus, each abstract algorithm is converted into a function written in \( \ires \)
through the algorithm compiler. For example, Figure~\ref{fig:to-primitive-ires}
describes the generated \( \ires \) function for the \( \code{ToPrimitive} \)
algorithm. The \( \code{input} \) and \( \code{PreferredType} \) are parameters
of the \( \code{ToPrimitive} \) function. The parameter \( \code{PreferredType} \)
is might be optional but we handle such cases with a special value \( \code{absent} \).
The \( \code{absent} \) value denotes that it is not present.
Thus, the condition of the step 2-a is converted into
the equality check with the \( \code{absent} \).
For the assertions, we omit in this paper but we believe that it could be handled in
the same approach. The specific keywords will be represented as string values.
For instance, the hint Number or the hint String converted into \( \code{"Number"} \)
and \( \code{"String"} \). Moreover, the algorithm compiler modifies prefixes of
symbols from @@ to \( \code{SYMBOL\_} \) and handle exceptions with the corresponding
intrinsic error objects.

@@

From now, we describe the detailed techniques of \( \tool \).
Section~\ref{sec:parser} formallly defines \( \bnfes \) and how to automatically
generate parsers from given \( \bnfes \) using lookahead parsers.
Section~\ref{sec:compiler} explains abstract algorithms with tagged tokens
and how to compile them into \( \ires \) functions based on
given conversion rules. Moreover, we introduce the rule generation assistant
to easily construct conversion rules. Section~\ref{sec:framework} describes
the implemented details including global settings to evaluate JavaScript programs.
Section~\ref{sec:eval} discusses the effectiveness of \( \tool \) with
four research questions.
Section~\ref{sec:related} discusses related work and Section 8 concludes.

>>>>

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/array_literal.png}
    \caption{\( ArrayLiteral \) production.}
    \label{fig:array-literal-es}
  \end{subfigure}
  \begin{subfigure}[t]{0.48\textwidth}
    \begin{lstlisting}[style=myScalastyle]
type P[T] = List[Boolean] => LAParser[T]
lazy val ArrayLiteral: P[ArrayLiteral] = memo {
  case List(Yield, Await) =>
  "[" ~ opt(Elision) ~ "]" ^^ ArrayLiteral0 |
  "[" ~ ElementList(Yield, Await) ~ "]" ^^ ArrayLiteral1 |
  "[" ~ ElementList(Yield, Await) ~ "," ~ opt(Elision) ~ "]" ^^ ArrayLiteral2
}
    \end{lstlisting}
    \caption{The generated parser for \( ArrayLiteral \) production.}
    \label{fig:array-literal-parser}
  \end{subfigure}
  \caption{\( ArrayLiteral \) production in ECMAScript 2020 specification and its generated parser.}
  \label{fig:array-literal}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}{0.4\textwidth}
    \includegraphics[width=\textwidth]{img/to_primitive.png}
    \subcaption{The ToPrimitive abstract algorithm.}
    \label{fig:to-primitive-es}
  \end{subfigure}
  \qquad
  \begin{subfigure}{0.48\textwidth}
    \begin{lstlisting}[style=ires]
"ToPrimitive" (input, PreferredType) => {
  if (= (Type input) "Object") {
    if (= PreferredType absent) let hint = "default"
    else if (= PreferredType "String") let hint = "string"
    else let hint = "number"
    let exoticToPrim = ? (GetMethod input SYMBOL_toPrimitive)
    if (! (= exoticToPrim undefined)) {
      let result = ? (Call exoticToPrim input (new [hint]))
      if (! (= (Type result) "Object")) return result
      return (Throw INTRINSIC_TypeErrorPrototype)
    }
    if (= hint "default") hint = "number"
    return ? (OrdinaryToPrimitive input hint)
  }
  return input
}
    \end{lstlisting}
    \subcaption{The \( \ires \) funciton for the ToPrimitive algorithm.}
    \label{fig:to-primitive-ires}
  \end{subfigure}
  \caption{ToPrimitive abstract algorithm in ECMAScript 2020 specification and its generated \( \ires \) function.}
  \label{fig:to-primitive}
\end{figure*}

@@

The semantics in ECMAScript specifications are described as
abstract algorithms. They are written in structured natural languages
with ordered steps and tagged tokens. The spec extractor extracts each abstract algorithm
with HTML tags because we utilize tag information to discriminate different kinds of tokens.
For example, Figure~\ref{fig:to-primitive-es} is the ToPrimitive
abstract algorithm in ECMAScript 2020. It has three steps and
second step consists of seven sub-steps. Each parameter or local variable such as
\( \code{input} \) or \( \code{PreferredType} \) is written with \( \code{<var>} \) HTML tags
and each value is tagged with \( \code{<code>} \).

To extract such abstract algorithms into treatable representations,
we define \( \ires \), a specialized intermediate representation
for ECMAScript abstract algorithms. Then, we develop the \textit{algorithm compiler}
in Scala using also Scala parser combinators to convert given abstract algorithms
into \( \ires \) functions. It is dependent on the compile rules that consists of two parts;
parsing rules and mapping from each rule into \( \ires \) component.
We explain detailed role of compile rules in Section~\ref{sec:compiler}.
Thus, each abstract algorithm is converted into a function written in \( \ires \)
through the algorithm compiler. For example, Figure~\ref{fig:to-primitive-ires}
describes the generated \( \ires \) function for the ToPrimitive
algorithm. The \( \code{input} \) and \( \code{PreferredType} \) are parameters
of the \( \code{ToPrimitive} \) function. The parameter \( \code{PreferredType} \)
is might be optional but we handle such cases with a special value \( \code{absent} \).
The \( \code{absent} \) value denotes that it is not present.
Thus, the condition of the step 2-a is converted into
the equality check with the \( \code{absent} \).
For the assertions, we omit in this paper but we believe that it could be handled in
the same approach. The specific keywords will be represented as string values.
For instance, the hint Number or the hint String converted into \( \code{"Number"} \)
and \( \code{"String"} \). Moreover, the algorithm compiler modifies prefixes of
symbols from @@ to \( \code{SYMBOL\_} \) and handle exceptions with the corresponding
intrinsic error objects.

@@

From now, we describe the detailed techniques of \( \tool \).
Section~\ref{sec:parser} formallly defines \( \bnfes \) and how to automatically
generate parsers from given \( \bnfes \) using lookahead parsers.
Section~\ref{sec:compiler} explains abstract algorithms with tagged tokens
and how to compile them into \( \ires \) functions based on
given compile rules. Moreover, we introduce the rule generation assistant
to easily construct compile rules. Section~\ref{sec:framework} describes
the implemented details including global settings to evaluate JavaScript programs.
Section~\ref{sec:eval} discusses the effectiveness of \( \tool \) with
four research questions.
Section~\ref{sec:related} discusses related work and Section 8 concludes.
